---
title: "Incarceration Analysis"
date : "2/25/2022"
name : "Tracy Chan"
output: html_document
---

```{r setup, include=FALSE}
library("ggplot2")
library("dplyr")
knitr::opts_chunk$set(echo = TRUE)
```



**Introduction:**

  For this assignment we are looking into a data set of different incarceration trends over time. The first variable I am choosing to analyze is the `black_jail_pop`. I chose this variable since I think that it has significant trends in the data set I think that you will be able to see certain trends within this variable since after watching the documentary it talked about a lot of racism towards black citizens as they did not have a high social class and officers were blaming lots of crimes on the black citizens. I am also going to analyze the `white_jail_pop` I want to compare this to the `black_jail_pop`, so in my variables I did the total `white_jail_pop`, and total `black_jail_pop`. Then I wanted to see the total number of `female_jail_pop` vs the `male_jail_pop` you can see a significant difference in the numbers of the two. I also wanted to see the `black_female_jail_pop` in TX and compare it to the `white_female_jail_pop` and surprisingly the outcomes for the two were totally not what I guessed it would be, the black female jail population would be a lot more than the white female jail population. I also wanted to know what state had the highest `black_jail_pop` and which state had the highest `white_jail_pop` and I found that New York had the highest black jail population, while California had the highest white male jail population which was very surprising to me.
  
  
**Comparison**
  
**Maps**

```{r, echo=FALSE, message=FALSE, warning=FALSE}

library(leaflet)
library(tidyverse)
library(ggmap)
library(leaflet.extras)
library(maps)
library(leaflet)
library(ggplot2)
library(mapdata)
library(mapproj)
library(htmltools)


County <- ("https://raw.githubusercontent.com/vera-institute/incarceration-trends/master/incarceration_trends.csv")
County_level_csv <- read.csv(County, header = TRUE)
View(County_level_csv)


s <- map_data('state')
ggplot(s, aes(x = long, y = lat, group = group) ) + 
  geom_polygon(color = 'pink') + 
  coord_map('polyconic')

```

**Trends** 



